% !TeX root = ../main.tex
\section{Discussions and Conclusions}

\subsection{Feasibility of Embedded Soccer Analysis}

The main focus of this work was analysing whether a full-stack soccer analysis system could be compressed and deployed on a low-cost edge device such as the Jetson Orin Nano, in a manner practically useful for real-world applications. The results indicate that this is likely feasible with the current generation of embedded hardware, but that achieving the target throughput of 20~FPS will require further system-level engineering optimisations rather than additional model compression. Figures \ref{fig:sweep_new_map1_5_vs_latency} and \ref{fig:piechart_latency_breakdown} support this conclusion most directly, indicating that the compressed full-stack systems can operate within 15\% of the prior baselines, at a throughput of 12--13 FPS and an end-to-end latency of 90.6~ms. This represents a substantial improvement over both the uncompressed configuration, which achieved fewer than 3 FPS on the same hardware during early development, and prior implementations in the literature, several of which produced fewer than 1 FPS on equivalent hardware. 

From a hardware resource perspective, the deployed system operated well within the constraints defined in Section~3.3.2. GPU utilisation averaged \textbf{40--55\%}, power draw \textbf{2--5~W}, and device temperature \textbf{48--56\textdegree C}, against respective limits of 80\%, 20~W, and 68\textdegree C. This indicates that the system is not at risk of dangerous power or thermal limits. Instead, this shows that further performance improvements remain achievable within the existing hardware budget through additional compression or system-level parallelisation.

The biggest current concern to complete feasibility is FPS, as expected. While the compressed system achieved the minimal goal of 100ms latency (10 FPS), the ideal target of 20 FPS was not met. Results indicate that object detection is still the likely bottleneck, accounting for 47\% of the total latency in the compressed configuration, with pitch keypoint estimation accounting for 31\% and post-inference processing for 22\%. This suggests that further optimisations should be targeted primarily at the object detection component, though improvements to the post-inference pipeline may also yield meaningful throughput gains. 

\subsection{Compression Technique Effectiveness}

Compression analysis across the \textbf{904} produced models reveals consistent patterns in how individual techniques affect inference latency and accuracy across both object and pitch keypoint locatisation. The most clear finding is that hardware acceleration and FP16 quantisation offer very little downside across all tasks and model sizes, while more aggressive techniques, including INT8 quantisation, input resolution scaling, and structured pruning, produce more varied trade-offs that require individual evaluation. The following subsections examine these patterns at the level of model architecture, scale, and individual technique.

\subsubsection{YOLO11 versus YOLO26}

The key analysis of choosing YOLO11 versus YOO26 models is whether the small architectural differences as discussed in the literature review produce meaningful differences, both in compressed and uncompressed forms.



For object detection, the uncompressed YOLO26 models consistently achieved marginally higher mAP\textsubscript{50--95} than YOLO11 at equivalent medium-to-large scales, with YOLO26l and YOLO26x reaching 0.928 and 0.929 respectively against 0.907 and 0.896 for their YOLO11 counterparts. At the nano scale this relationship inverts, with YOLO11n achieving 0.857 against 0.842 for YOLO26n, suggesting that the benefits of YOLO26's Progressive Loss Balancing and Small-Target-Aware Label Assignment compound with model capacity and are not realised in capacity-constrained architectures. For pose estimation, results were broadly comparable between families at small and medium scales, with the notable exception of YOLO26n-pose, which substantially outperformed YOLO11n-pose at 0.993 against 0.923 mAP\textsubscript{50--95} and is discussed separately in Section~7.2.7. At equivalent scales, inference latency was near-identical across both families, and model family selection should therefore be driven by accuracy requirements rather than latency considerations.

For the most part, the effect of compression was similar across YOLO11 and YOLO26 models. Both families responded similarly to hardware acceleration and FP16 quantisation. Under INT8 quantisation, YOLO26 exhibited slightly greater accuracy retention at medium and large object detection scales, consistent with its improved training signal producing weight distributions more amenable to aggressive precision reduction. The most pronounced divergence arose under pose model pruning: YOLO11-pose pruning was achievable across most scale combinations with recoverable accuracy following fine-tuning, whereas YOLO26-pose pruning produced training instability across multiple configurations and was omitted from the analysis entirely. The architectural source of this instability was not investigated within the scope of this work.

Overall, YOLO26 is the preferable family for medium-to-large object detection deployments where compression is limited to hardware acceleration and FP16 quantisation. YOLO11 offers a more stable platform for aggressive compression pipelines, particularly those involving structured pruning of pose estimation models.

\subsubsection{Effect of Model Scale on Compression}

The five YOLO scale variants differ in depth and width scaling, producing systematic variation in parameter count, computational cost, and representational capacity \cite{UltralyticsYOLO}. At baseline, object detection accuracy increased monotonically from nano to medium scale, with diminishing returns beyond that point --- YOLO11l and YOLO11x both underperformed YOLO11m on the Football Analytics dataset, suggesting the dataset does not provide sufficient training signal to fully exploit the capacity of the largest variants. Pose estimation accuracy was consistently high across all scales, with most uncompressed variants exceeding 0.97 mAP$_{50\text{--}95}$.

Under compression, scale interacted with each technique differently. Hardware acceleration and FP16 quantisation were robust across all scales, though the latency benefit of acceleration scaled positively with model size --- YOLO11x saw a 36.0\% latency reduction versus only 14.5\% for YOLO11n. INT8 quantisation was more damaging at smaller scales for object detection, where models possess less numerical redundancy, and was severely damaging for pose estimation at nearly all scales. Input resolution reduction produced broadly comparable relative degradation across object detection scales, but was destructive for pose estimation regardless of scale. Pruning was more viable at larger scales, where greater representational redundancy exists; at nano and small scales, even conservative 90\% weight retention produced non-trivial accuracy losses, and pruning should therefore be considered primarily for medium-to-large variants.

For practical deployment, the YOLO26s and YOLO26m variants represent the most favourable operating points for object detection, offering strong accuracy that is well-maintained under FP16 quantisation and 75\% resolution scaling. Nano variants are appropriate where latency is the dominant constraint but should not be subjected to INT8 quantisation or aggressive pruning. Large and extra-large variants are unlikely to be justified given the diminishing accuracy returns observed relative to the medium variant. For pose estimation, YOLO26n-pose is the recommended default, combining high uncompressed accuracy with exceptional compression robustness relative to all other pose variants examined.

\subsubsection{Compression Technique Effectiveness Summary}

Across all model families, scales, and tasks, hardware acceleration and FP16 quantisation emerged as the most broadly effective techniques, delivering latency reductions of 31--43\% with negligible accuracy cost. These two techniques share a common basis in that neither modifies learned representations destructively, and should be treated as mandatory first steps in any edge deployment pipeline rather than optional enhancements.

Beyond these, a clear divergence emerged between object detection and pose estimation under more aggressive compression. Object detection tolerated input resolution reduction at 75\%, INT8 quantisation at medium-to-large scales, and moderate pruning at acceptable accuracy costs. Pose estimation was considerably more sensitive to all three techniques --- INT8 quantisation alone reduced pose mAP$_{50\text{--}95}$ by 43.8\% on average, resolution reduction below 75\% caused severe degradation, and pruning produced disproportionate accuracy penalties relative to the latency gains achieved. This sensitivity reflects the dependence of keypoint localisation on fine-grained spatial representations that are disproportionately disrupted by precision reduction, downsampling, and weight removal --- a qualitative difference in task requirements that has direct practical implications for compression strategy selection in multi-task pipelines.

Knowledge distillation provided no meaningful standalone latency benefit when evaluated against hardware-accelerated baselines, consistent with its theoretical basis of improving learned representations rather than altering network structure. Its primary value was as a supporting technique: the Distill+Prune+Accelerated combination recovered much of the accuracy lost through pruning, achieving only $-$0.1\% mAP$_{50\text{--}95}$ for pose models at an 11.1\% latency improvement, demonstrating that distillation is best understood as an accuracy preservation mechanism rather than a direct compression method.

\subsection{Best Model and Compression Pathway}

The compression results collectively suggest that the most effective deployment strategy is not the application of a single aggressive technique, but rather the sequential layering of low-cost optimisations before resorting to more invasive methods. Hardware acceleration and FP16 quantisation recover a substantial portion of the available latency budget at near-zero analytical cost, meaning that in many cases no further compression is necessary to meet deployment constraints. This is a practically important finding: it implies that the compression problem for this class of model on this hardware is largely solved by deployment-stage optimisations alone, without requiring any modification to the trained model itself.

Where further compression is needed, the choice of technique should be driven by task type rather than applied uniformly. Object detection models are considerably more tolerant of structural and numerical compression, and practitioners can reasonably consider input resolution reduction, moderate pruning, or INT8 quantisation as secondary steps. Pose estimation models, by contrast, should be treated as fragile under any technique that disrupts spatial precision --- the results suggest that FP16 quantisation represents close to the limit of safe compression for this task in most configurations, with the notable exception of distillation-assisted pruning which demonstrated that accuracy losses from pruning can be substantially recovered when the two techniques are combined. This asymmetry between tasks is arguably the most practically significant finding of the compression study, as it implies that a one-size-fits-all compression strategy is inappropriate for multi-task pipelines of this kind.


\subsection{Full-Stack System}

The full-stack system satisfied its primary accuracy objective, with the best achieved pass mAP\textsubscript{1--5} of 69.7\% falling within the 15\% criterion specified in Section~3.3.3. This result is substantively meaningful given that the system operates in real time on a device drawing under 5~W of power, in contrast to the server-grade infrastructure on which the SoccerNet baseline was evaluated.

The throughput result of 12--13~FPS requires contextualisation. The latency decomposition presented in Figure~24 reveals a structural shift not apparent from model-level benchmarks: compression has displaced the system bottleneck. In the uncompressed configuration, pitch keypoint estimation accounted for 64.2\% of total system latency, with object detection contributing 31.1\%. In the compressed configuration, keypoint estimation has been reduced to 31.0\%, while post-inference processing and team assignment have grown substantially in relative proportion. The compression work has therefore been largely successful on its own terms; the principal constraint on further throughput improvement is the non-inference pipeline rather than model inference itself.

This finding carries direct implications for future system design. The post-inference pipeline --- encompassing homography estimation, ByteTrack multi-object tracking, K-means-based team assignment, and statistic generation --- was implemented with analytical correctness and interpretability as primary objectives, appropriate given the scope of this work. However, these components now represent the primary engineering target for closing the gap between the achieved 12--13~FPS and the 20~FPS design target. Parallelising model inference with post-inference processing, reducing the frequency of homography updates, and implementing more computationally efficient clustering variants are tractable optimisations that require no modification of the trained models and are likely to yield meaningful throughput improvements.

The team assignment component additionally represents the weakest analytical link in the pipeline. Jersey colour clustering under broadcast lighting conditions is well-documented as sensitive to cast shadows, motion blur, and chromatic similarity between opposing kits~\cite{zheng2012}. The manual specification of team colours as a system parameter further constrains the pipeline's generalisability to unseen match footage. A dedicated lightweight jersey classification model, trained on labelled kit colour data, would likely improve both the accuracy and robustness of this component.

\subsection{Limitations}

Several methodological limitations qualify the findings presented in this thesis.

\textbf{Post-training compression throughout.} Quantisation, input resolution scaling, and pruning were applied post-training throughout, without retraining at the target configuration. This was a deliberate methodological choice to isolate the effect of each technique and maintain a sustainable experimental scope across the full inventory of 904 model artefacts. Consequently, particularly aggressive compression settings --- including INT8 quantisation for pose estimation models, 50\% resolution scaling, and 70\% weight retention pruning --- represent pessimistic lower bounds on achievable performance. Quantisation-aware retraining and resolution-native training may recover a meaningful proportion of the accuracy losses observed under these conditions.

\textbf{Knowledge distillation evaluation.} As noted in Section~6.3, the latency measurements for PyTorch-based distilled models are inflated by inefficiencies in the distillation training loop. While evaluation of exported engine variants partially mitigates this artefact, it conflates the contribution of distillation with that of hardware acceleration, preventing clean isolation of the distillation effect. The conclusions drawn regarding knowledge distillation should accordingly be treated as indicative rather than definitive.

\textbf{Hardware telemetry granularity.} Hardware performance metrics were collected via the NVIDIA \texttt{tegrastats} utility at a polling interval of 200~ms. Short-duration spikes in GPU utilisation and power draw occurring between polling events will not be captured in the reported averages. Individual model benchmarks conducted under sustained continuous inference, reported in Figures~26 and~27, provide a more reliable characterisation of peak resource consumption.

\textbf{Single edge device.} All benchmarking was conducted exclusively on an NVIDIA Jetson Orin Nano Dev Kit operating in MAXN mode. The reported latency, GPU utilisation, and power draw characteristics are specific to this platform and its associated TensorRT implementation, and cannot be assumed to generalise to other edge platforms without repeating the full export and benchmarking procedure on the target hardware.

\textbf{Full-stack evaluation scope.} Pass mAP\textsubscript{1--5} was evaluated on a single continuous ten-minute broadcast video for each model combination. While this provides a consistent and reproducible comparative basis, it limits the generalisability of the absolute accuracy figures to alternative matches, camera perspectives, lighting conditions, and kit colour combinations.

\textbf{YOLO26-pose pruning instability.} Pruning results for the YOLO26-pose model family are omitted from the analysis due to training instability encountered during fine-tuning following channel removal. The underlying cause was not investigated within the scope of this work, and the pruning conclusions for pose estimation models are therefore grounded solely in YOLO11-pose experimental evidence.