% !TeX root = ../main.tex
\section{Impact of Research}

The research presented in this thesis has the potential to deliver impact across both the sports technology industry and the wider field of embedded computer vision, both in terms of ease of technical acsess, and in sustainability. Historically, advanced soccer analytics --- such as real-time formation tracking, possession estimation, and pass detection --- have been the exclusive domain of professional clubs and broadcasters, relying on expensive multi-camera infrastructure and cloud-based processing pipelines. By demonstrating that a full-stack analysis system can run effectively on a low-cost edge device such as the NVIDIA Jetson Orin Nano, this work lowers the barrier to entry for clubs, coaches, and analysts operating without access to enterprise-grade resources. The compression technique analysis also provides information on how to lower computational and resource costs, reducing consumption and environmental impact. 

\subsection{Potential Beneficiaries and Pathways to Impact}

The first and most direct potential beneficiares of this research are football clubs, coaches, and analysts at the amateur and semi-professional levels. These groups often lack access to the high-end analytics tools used by elite teams, but could benefit greatly from affordable systems that provide insights into player positioning, team formations, and tactical patterns. By enabling real-time analysis on embedded hardware, this work could empower smaller clubs to make data-driven decisions during matches and training sessions without needing expensive infrastructure or cloud services. 

Another potential beneficiary group includes sports technology companies and developers of computer vision systems for sports analytics, including those beyond just soccer. The findings on model compression techniques and hardware acceleration can inform the design of more efficient algorithms and systems, leading to products that are both powerful and accessible. The research could also inspire further innovation in edge-based sports analytics, encouraging the development of new applications and features that leverage real-time insights.

The final potential beneficiary group is the broader research community in computer vision and embedded systems. The detailed analysis of compression techniques and their impact on latency and accuracy can serve as a valuable reference for researchers working on similar problems in other domains, such as surveillance, robotics, or autonomous vehicles. The methodologies and findings could be applied to a wide range of applications where real-time performance on resource-constrained devices is critical.

\subsection{Ethical Considerations and Risk Mitigation}

While the potential benefits of this research are clear, it is also important to consider the ethical implications of deploying computer vision systems in sporting environments, as well as the training and compression processes. The most notable of these concerns is that of privacy, as a system capable of real-time player detection, tracking, and positional analysis raises quaestions about the continuous tracking of individuals, raising questions about consent, data ownership, and the potential for misuse. This is particularly relevant in amateur and semi-professional contexts, where players may not have formally consented to being analysed, and where robust data governance frameworks are less likely to be in place compared to professional organisations. This ethical concern is mitigated by ensuring that any tracking data does not attempt to identify indivduals by number or position or name, and instead focuses on aggregate team-level insights. 

A second ethical consideration concerns the potential for performance data to be used in ways that are harmful to players. Granular tracking data — such as positioning, movement patterns, and involvement in play — could be used to unfairly scrutinise individual players, particularly at lower levels of the game where players participate recreationally. Care must be taken to ensure that any deployment of such systems is accompanied by transparent communication to all participants about how data is collected, stored, and used, and that appropriate data minimisation and anonymisation practices are followed where possible. Again, this is mitigated by ensuring that the system focuses on team-level insights rather than individual player performance, and by providing clear guidelines for responsible use of the data generated by the system.

The third and final ethical consideration concerns the datasets used for training. If images or video of players are used without appropriate consent or licensing, this can raise important privacy and ethical concerns. In this work, the primary object detection datasets sourced from SoccerNet \cite{tracking}, Football-Analytics\cite{roboflow_football_analytics_gnykk_model1}, and Roboflow\cite{roboflow} were compiled from footage drawn from the five major European football leagues, where such material is available for fair, non-commercial research use. As this project is academic in nature and not intended for commercial deployment, it remains within that scope. 
\subsection{Sustainability Considerations and Sustainable Development Goals}


At the direct level, the core aims of this thesis — deploying computer vision on edge hardware rather than relying on cloud-based inference — demonstrates the sustainability benefits. Cloud inference pipelines typically involve transmitting video data to remote data centres, where it is processed on high-powered GPU clusters that consume significant energy and contribute to carbon emissions. By contrast, the NVIDIA Jetson Orin Nano operates at a fraction of the power draw of a server-grade GPU, and the compression techniques explored in this thesis reduce that footprint further. As shown in the results, quantisation alone reduced average power draw by over \textbf{40\%} across both object detection and pose estimation tasks. At scale, the difference between a cloud-dependent and an edge-based deployment represents a meaningful reduction in energy consumption per analysed match.

Beyond the system itself, the compression methodology developed in this thesis contributes to a broader trend of sustainable AI development. The field of deep learning has faced scrutiny over the energy cost of training and deploying large models. This work demonstrates that smaller, compressed models can retain the vast majority of their analytical utility, providing a concrete example of how performance and efficiency need not be in opposition. This aligns directly with the principles of green AI and responsible machine learning, which advocate for minimising computational resource usage without sacrificing meaningful capability.

In terms of the United Nations Sustainable Development Goals \cite{un_sdgs}, this research most directly supports \textbf{SDG 9: Industry, Innovation and Infrastructure}, as it involves developing efficient technological infrastructure (compressed computer vision on edge). It also contributes to \textbf{SDG 13: Climate Action}, as reducing the energy footprint of these computer vision systems contributes towards lowering the carbon use of digital infrastructure. Finally, the increasing of access to cheap sports analytics aligns with \textbf{SDG 10: Reduced Inequalities}, by making tools previously available only to well-resourced professional clubs accessible to amateur and semi-professional organisations with limited budgets.