% !TeX root = ../main.tex
\section{Lay Abstract}

This work examines whether modern computer vision methods for soccer analysis can be compressed to run directly on compact, low-power hardware, without relying on costly external infrastructure. Two core tasks were explored: detecting objects such as the players and the ball, and identifying the lines and markings on the pitch. In total, \textbf{904} model variants were trained and benchmarked across several optimisation methods, including hardware acceleration, quantisation, pruning, and knowledge distillation.

Results show that hardware acceleration and reduced numerical precision (quantisation) delivered the largest speed improvements with little loss in detection quality for player and ball tracking. Pitch marking detection proved considerably more unstable under the same techniques, degrading sharply when compression was applied aggressively. This suggests that identifying precise field geometry allows less compression than ball and player spotting.

The best models were integrated into a full system that estimates possession, passes, and generates formation maps from broadcast footage on a compact portable device. The strongest configurations offereed accuracies within 15\% of existing server-based systems, while consuming under 20W of power and processing footage at approximately 13 frames per second. This demonstrates that useful, real-time soccer analytics is achievable on hardware compact enough for pitchside deployment.